Experience Report: Haskell in Computational Biology

### 2012-03-11 mrfy_experience_report.tex
sketch of what NR is looking for in comparison section

\emph{[Alternate introduction, trying to tie the points more closely
to the content of the paper:\\
In~this paper, we report on an attempt to replace both these families
of languages with Haskell: 
\begin{itemize}
\item
Although had to write a new implementation of a standard
algorithm, the cost was low, and the connection between code and
algorithm is unusually strong (\secref{viterbi}).
The performance of our new implementation is comparable to the
performance of~C++ (\secref{perf}).
\item
As expected, higher-order functions made it unusually easy to
implement and experiment with a family of related algorithms
(\secref{hofs}).
\item
Haskell is surrounded by a penumbra of libraries and tools that
promise powerful abstractions.
Some deliver very high leverage, but others are not ready for prime
time (\secref{penumbra}).
We~found it difficult to tell which is which in advance.
\item
It is possible to use Haskell successfully for research even with a
very modest background in functional programming. We found our Haskell
implementation to be more flexible about adding new research ideas
than our past C++ code (\secref{comparo}).
\item
The only significant impediment that Haskell has presented to our
research has been the difficulty of understanding and tuning the
performance of Haskell programs.
\end{itemize}
]}

@@

\subsection{Performance}
\seclabel{perf}

@@

\section{Our previous experience compared}
\seclabel{comparo}

>>>>

\emph{[Alternate introduction, trying to tie the points more closely
to the content of the paper:\\
In~this paper, we report on an attempt to replace both these families
of languages with Haskell: 
\begin{itemize}
\item
Although had to write a new implementation of a standard
algorithm, the cost was low, and the connection between code and
algorithm is unusually strong (\secref{viterbi}).
The performance of our new implementation is comparable to the
performance of~C++.
\item
As expected, higher-order functions made it unusually easy to
implement and experiment with a family of related algorithms
(\secref{hofs}).
\item
Haskell is surrounded by a penumbra of libraries and tools that
promise powerful abstractions.
Some deliver very high leverage, but others are not ready for prime
time (\secref{penumbra}).
We~found it difficult to tell which is which in advance.
\item
It is possible to use Haskell successfully for research even with a
very modest background in functional programming. 
\item
The only significant impediment that Haskell pas presented to our
research has been the difficulty of understanding and tuning the
performance of Haskell programs.
\end{itemize}
]}

@@

\subsection{Performance}

@@

\section{Our previous experience compared}
